\cvsection{Projects}
\begin{cventries}
  \cventry
    {}
    {Research on Short Text Classification with Naive Bayes Algorithm}
    {Shanghai,China}
    {Sep. 2015 - Jun.2016}
    {
      \begin{cvitems}
      \vspace{-10pt}
        \item {Deployed LAMP environment on Ali-cloud elastic server. Then Deployed Joomla Framework on webserver}
        \item {Crawled pages of secondhand board of SJTU BBS website with crawler written in Python. Stored pages in local HBase database.}
        \item{Developed Naive Bayes algorithm with C++. Used part of text titles to train the algorithm. Analyzed accuracy of Naive Bayes algorithm. Compared classification accuracy Naive Bayes algorithm with SVM.}
        \item{Deployed crawler and model on webserver. Used Android App to visit server. Transfer classified data in JSON format to Android App.}
        \item{Relevant Skills:Python, Java,C++, Crawler, HBase, Naive Bayes algorithm, SVM, LAMP, App Develop}
      \end{cvitems}
      }
  \cventry
    {}
    {Take out Food Ranking Website Develop}
    {Shanghai, China}
    {Sep. 2015 - Jun. 2016}
    {
      \begin{cvitems}
      \vspace{-10pt}
        \item {Crawled raw pages of Eleme, Meituan and Baidu Take Out around SJTU and stored all raw pages into HBase}
        \item {Wrote MapReduce program to extract information like food name, sales, price and so on. Then used  <Key,Value> structure of MapReduce to rank.}
        \item {Uploaded results of ranking to Ali-cloud server. Developed webpages with PHP to display ranking results.}
        \item {Used statistical method and Linear regression method, etc to analyze factors' influence like discount, freight fee, price and positions in website and so on on sales.}
        \item{Relevant Skills:Java, MapReduce, HBase, sklearn, Numpy, Pandas, website develop}
      \end{cvitems}
    }
    \cventry
    {}
    {Research of Applications of Big Data Analyzation Technology on Status Estimation of Power Transmission Equipment}
    {Shanghai, China}
    {Sep. 2015 - Present}
    {
      \begin{cvitems}
      \vspace{-10pt}
        \item {Used local PC and VM to deploy Hadoop cluster. Deployed HBase on top of Hadoop.}
        \item {Constructed data model to store complex data of State Grid.  The Model supports JOIN operation, which HBase doesn't support. Use secondary index method to support transactions of State Grid.}
        \item{Publicated an academic paper A Versatile Event-Driven Data Model in HBase for Multi-Source Data of Power Grid}
        \item{Relevant Skills:Java, Hadoop, HBase, Data Model, Secondary Index, Transaction Oriented Program}
      \end{cvitems}
    }

%  \cventry
%    {Member}
%    {MSSA (Management Strategy Club of POSTECH)}
%    {Pohang, S.Korea}
%    {Sep. 2013 - PRESENT}
%    {
%      \begin{cvitems}
%        \item {Gained knowledge about several business field like Management, Strategy, Financial and marketing from group study.}
%        \item {Gained expertise in business strategy areas and inisght for various industry from weekly industry analysis session.}
%      \end{cvitems}
%    }
\end{cventries}
